---
title: "Week 4 Assignment for Shiny App"
author: "Chien-Hua Wang"
date: "04/06/2019"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

Using Shiny App development tool to create the data product and demonstrate the pattern for diamond's data.
Therefore, we could through this design to predict the price by specific requirements. 

Furthermore, we provided relative links for readers to get deeper inside the tool's design.

## Tool Description
- Diamonds Properties can be analysed using several Parameters.

- Carat,Price,sample size,color Depth are some of the common parameters.

- This Report enables to pick the right parameters for the best Diamond selection.

- Final function is to predict the relative price for those parameters.

## Dataset Overview
```{r, echo=FALSE}
head(diamonds)
```

## Attribute's structure
```{r, echo=FALSE}
str(diamonds)
```

## Interactive Plot
```{r eruptions, fig.align='center', fig.pos='H'}
# Define UI for application that draws a histogram
shinyUI(fluidPage(
  
  # Application title
  titlePanel("Price predictor for Diamonds"),
  
  # Sidebar with options selectors
  sidebarLayout(
    sidebarPanel(h3(helpText("Select:")),
      numericInput("car", label = h4("Carats"), step = 0.01, value = 1.5),
      selectInput("cut", label = h4("Cut"),
                  choices = list("Unknown" = "*", "Fair" = "Fair", "Good" = "Good",
                                 "Very Good" = "Very Good", "Premium" = "Premium",
                                 "Ideal" = "Ideal")),
      selectInput("col", label = h4("Color"),
                  choices = list("Unknown" = "*", "D" = "D", "E" = "E",
                                 "F" = "F", "G" ="G",
                                 "H" = "H", "I" = "I",
                                 "J" = "J")),
      selectInput("clar", label = h4("Clarity"),
                  choices = list("Unknown" = "*", "I1" = "I1", "SI2" = "SI2",
                                 "SI1" = "SI1", "VS2" = "VS2", "VS1" = "VS1",
                                 "VVS2" = "VVS2", "VVS1" = "VVS1", "IF" = "IF" ))
    ),
    
    #Show Plot and Predicted Value of Diamond:
    mainPanel(
      plotOutput("distPlot"),
      h4("Predicted value of this diamond is:"),
      h3(textOutput("Predicted_Value"))
    )
  )
))
library(shiny)
library(ggplot2)
library(dplyr)
library(rsconnect)
# Select columns to be used in the analysis
diam <- diamonds[,c(1:4,7)] 
# Define server logic required to draw a plot
output$distPlot <- renderPlot({
    # Select diamonds depending of user input
    diam <- filter(diamonds, grepl(input$cut, cut), grepl(input$col, color), grepl(input$clar, clarity))
    # build linear regression model
    fit <- lm( price~carat, diam)
    # predicts the price
    pred <- predict(fit, newdata = data.frame(carat = input$car,
                                              cut = input$cut,
                                              color = input$col,
                                              clarity = input$clar))
    # Draw the plot using ggplot2
    plot <- ggplot(data=diam, aes(x=carat, y = price))+
      geom_point(aes(color = cut), alpha = 0.4)+
      geom_smooth(method = "lm")+
      geom_vline(xintercept = input$car, color = "blue")+
      geom_hline(yintercept = pred, color = "blue")
    plot
  })
  output$Predicted_Value <- renderText({
    # Renders the text for the prediction below the graph
    diam <- filter(diamonds, grepl(input$cut, cut), grepl(input$col, color), grepl(input$clar, clarity))
    fit <- lm( price~carat, diam)
    pred <- predict(fit, newdata = data.frame(carat = input$car,
                                              cut = input$cut,
                                              color = input$col,
                                              clarity = input$clar))
    res <- paste(round(pred, digits = 1.5),"$" )
    res
  })
```



